### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

\begin{figure}[tb!]
	%\vspace{-1ex}
	\begin{center}
		\includegraphics[scale=1.28]{./fig/consistency_motivation.eps}
	\end{center}
	\vspace{-3ex}
	\caption{Pattern graphs}
	\vspace{-4ex}
	\label{fig-consistency-example}
\end{figure}

\revise{
We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}

\stitle{Pattern satisfiability}.
Given a pattern $P$, \grouprec firstly checks whether $P$ is satisfiable. We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P$ matches $G$ via team simulation, \ie $P \eeps G$.

Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
pattern graphs may be unsatisfiable for team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
%\looseness=-1

\begin{example}
\label{exm-consistency}
\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.

\sstab(2) Pattern $P_1$ in Fig.~\ref{exm-motivation} is satisfiable as $P_1 \eeps G_1$.
\end{example}

The good news is that checking the satisfiability of pattern graphs can be done in low polynomial time.

@@

\proofS By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$.
\eop

>>>>

\begin{figure}[tb!]
	%\vspace{-1ex}
	\begin{center}
		\includegraphics[scale=1.38]{./fig/consistency_motivation.eps}
	\end{center}
	\vspace{-3ex}
	\caption{Pattern satisfiability}
	\vspace{-4ex}
	\label{fig-consistency-example}
\end{figure}

In this section, we first study the pattern satisfiability problem for team formation, then introduce two  two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.

% with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.

\stitle{Pattern satisfiability}.
Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
there exist pattern graphs that do not match any data graph via team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
%\looseness=-1

\begin{example}
\label{exm-consistency}
\ni(1) For pattern $P_2$ in Fig.~\ref{fig-consistency-example},
one can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $v$ in $G$, if $v$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.

\sstab(2) However, pattern $P'_2$ in Fig.~\ref{fig-consistency-example} is satisfiable as $P'_2 \eeps G_2$, and pattern $P_1$ in Fig.~\ref{exm-motivation} is also satisfiable as $P_1 \eeps G_1$.
\end{example}

%Given a pattern $P$, \grouprec firstly checks whether $P$ is satisfiable.

We say that a pattern $P$ is {\em satisfiable} iff there exists a data graph $G$ such that $P$ matches $G$ via team simulation, \ie $P \eeps G$.
The good news is that checking the satisfiability of pattern graphs can be done in low polynomial time.

@@

By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Then pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are also small.

By Proposition~\ref{prop-pattern-consistency}, we shall consider  satisfiable pattern graphs only  in the sequel.
